### 2025-11-06 simulation.qmd
20251105 - more detail

1. Step 1—Design Grid: specify the fixed conditions to investigate in the simulation (e.g., sample size, generating distribution)
1. Step 2—Generate: specify how to generate the data for the simulation from the relevant probabilty distribution(s)
1. Step 3—Analyze: specify how to analyze the simulation data
1. Step 4—Summarize: specify how to summarize the results across the simulation replications
1. Step 5—Run the Simulation: run the simulation study (i.e., generate the data, analyze the simulated data, and summarize the results across the simulation replications)

@@

@@

First, we define what combinations of conditions to study, which is called our design grid.
In our simulation study, each player retains the same number of projections as they had in the original data, ensuring the simulation reflects real-world variation in data availability.
This number of projections defines our design grid.

```{r}
Design <- proj_dists_tbl %>%
  dplyr::mutate(
    id,
    n_sources = n_proj,
    .keep = "none"
  )
```

@@

Second, we generate the data for the simulation from the relevant probabilty distribution function(s).
In this case, we use a normal distribution or skew-normal distribution as our probability distribution function for a given player, depending on which distribution fits better to that player's distribution of projected points across sources (stored in `dist_info$type`).

@@

Third, we analyze the simulated data.

@@

Fourth, we summarize the results across the simulation replications.

@@

monteCarloSim_results <- SimDesign::runSimulation(
  design = Design,
  replications = 1000,
  generate = Generate,
  analyse = Analyse,
  summarise = Summarise,
  fixed_objects = list(proj_dists = proj_dists),
  seed = SimDesign::genSeeds(Design, iseed = 52242), # for reproducibility
  parallel = TRUE # for faster (parallel) processing
)
```

>>>>

1. Step 1—Design Grid: specify the fixed conditions to investigate in the simulation (e.g., sample size, generating distribution)
1. Step 2—Generate: specify how to generate the data for the simulation from the relevant probability distribution(s)
1. Step 3—Analyze: specify how to analyze the simulation data
1. Step 4—Summarize: specify how to summarize the results across the simulation replications
1. Step 5—Run the Simulation: run the simulation study (i.e., generate the data, analyze the simulated data, and summarize the results across the simulation replications)

@@

When designing a Monte Carlo simulation, @Sigal2016 (p. 151) recommend the following:

- beginning with a small number of replications and conditions (i.e., supplying a design object with fewer rows) to ensure that the code runs correctly, and increasing replications/conditions only when the majority of the bugs have been worked out
- documenting strange aspects of your simulation or code that you are likely to forget
- saving the state of your simulation in case of power failure or other mechanical failures (e.g., using the `save = TRUE` and/or `save_results = TRUE`, and/or `debug` arguments in `SimDesign::runSimulation()`), and, as necessary, performing debugging within a particular function (`debug` argument in `SimDesign::runSimulation()`)

@@

First, we define what combinations of conditions to study (with one row per each unique combination), which is called our design grid.
For the design grid, the columns are the design factors (e.g., sample size, generating distribution), and each row indicates a unique combination of the factors (e.g., *N* = 200, normal distribution; *N* = 500, normal distribution; *N* = 200, Poisson distribution; *N* = 500, Poisson distribution).
When we execute the simulation, each row of the design grid object will be run sequentially.

In our simulation study, each player retains the same number of projections as they had in the original data, ensuring the simulation reflects real-world variation in data availability.
This number of projections defines our design grid.
The design factors (columns) are the player (`id`) and the number of projections available for that player (`n_sources`).
The rows, then are the combinations of player and number of projections available for that player.

```{r}
Design <- proj_dists_tbl %>%
  dplyr::mutate(
    id,
    n_sources = n_proj, # number of projection sources available for player
    .keep = "none"
  )

Design
```

```{r}
#| include: false
#| eval: false

@@

Second, we generate the data for the simulation from the relevant probability distribution function(s).
In this case, we use a normal distribution or skew-normal distribution as our probability distribution function for a given player, depending on which distribution fits better to that player's distribution of projected points across sources (stored in `proj_dists[["INSERT_ID"]]$type`).
The `Generate()` function has a `condition` argument, which takes a single row from the design grid object (`Design`), and which controls the data generation for subsequent analysis.
We use the (optional) `fixed_objects` argument so we can pass an object that should be held constant across all simulation replications—i.e., a "fixed" object.
In this case, we pass—via the `proj_dists` object—the best-fitting distribution for each player (normal or skew-normal) to be used for all simulation replications.

@@

Third, we analyze the simulated data.
For each iteration of the simulation, the `Analyse()` function will return a vector with a requested variables: player (`id`), their simulated mean (`mean_pts`) and standard deviation (`sd_pts`) of projected fantasy points across sources, their the 10th (`q10`) and 90th (`q90`) quartiles of their distributions of projected points, and the simulated probability of the player scoring at least 100 (`p100`), 150 (`p150`), 200 (`p200`), 250 (`p250`), 300 (`p300`), and 350 (`p350`) fantasy points.
We then combine all the rows into a tibble dataframe, with each player as a different row.
A separate dataset is created for each of the simulation replications.

@@

Fourth, we summarize the results across the simulation replications.
In this case, we calculate—for each variable—each player's mean and standard deviation across the datasets from the different simulation replications.

Some potential metastatistics that can be computed include:

- mean: `base::mean()`
- standard deviation: `base::sd()`
- bias: `SimDesign::bias()`
- standardized bias: `SimDesign::bias(, type = "standardized")`
- relative bias: `SimDesign::bias(, type = "relative")`
- relative absolute bias: `SimDesign::RAB()` or `SimDesign::bias(, type = "abs_relative")`
- mean absolute error (MAE): `SimDesign::MAE()`
- normalized mean absolute error: `SimDesign::MAE(, type = "NMAE")`
- standardized mean absolute error: `SimDesign::MAE(, type = "SMAE")`
- root mean squared error (RMSE): `SimDesign::RMSE()`
- normalized root mean squared error: `SimDesign::RMSE(, type = "NRMSE")`
- standardized root mean squared error: `SimDesign::RMSE(, type = "SRMSE")`
- root mean squared log error (RMSLE): `SimDesign::RMSE(, type = "RMSLE")`
- integrated root mean squared error (IRMSE): `SimDesign::IRMSE()`
- mean-square relative standard error (MSRSE): `SimDesign::MSRSE()`
- coefficient of variation: `SimDesign::RMSE(, type = "CV")`
- relative efficiency: `SimDesign::RE()`
- empirical detection/rejection rate: `SimDesign::EDR()`
- empirical coverage rate: `SimDesign::ECR()`

@@

monteCarloSim_results <- SimDesign::runSimulation(
  design = Design,
  replications = 1000,
  generate = Generate,
  analyse = Analyse,
  summarise = Summarise,
  fixed_objects = list(proj_dists = proj_dists), # passing a list of objects that should be held constant across all simulation replications — i.e., "fixed" objects
  seed = SimDesign::genSeeds(Design, iseed = 52242), # for reproducibility
  parallel = TRUE # for faster (parallel) processing
)
```
